\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/experiments.tex
Update 25 Dec 11.00

This section presents several experiments to evaluate the performance of \FAMA and the quality of the learned models. Whenever applicable, we will consider scenarios with both known and unknown plan horizon to draw conclusions at both levels of complexity. We also devote one experiment to show the suitability of the novel evaluation metrics introduced in section \ref{sec:evaluation}.

\subsection{Setup}

@@

\subsection{Impact of the size of the input knowledge}

@@

Figure~\ref{fig:pspace_quality} displays \textcolor{red}{the average precision and recall of the 15 learned models} in the scenario with unknown plan horizon. As expected, the quality of the learned models is lower than when the horizon of the plan is known. \textcolor{red}{The higher complexity of this setting is also reflected in the appearance of some timeouts when solving the learning task. The first timeout is found in the \emph{grid} domain at $|\mathcal{T}| = 3$; the \emph{floortile} times out with $|\mathcal{T}| = 4$; and by the time $|\mathcal{T}|$ reaches 10 the number of domains were no solution is found is 6, adding the \emph{npuzzle, parking, rovers and zenotravel} domains.} We can observe in Figure~\ref{fig:pspace_quality} the opposite behaviour to Figure~\ref{fig:np_quality}; that is, we find a drop of the quality as the input knowledge increases. The drop in the score is caused by the increasing number of timeouts, meaning that no solution is found in many tasks within the given time-bound, and consequently a value of $0$ for precision and recall is assigned to these experiments. Figure \ref{fig:pspace_time}, on the other hand, reflects that the computation time of the first case study is also higher than in the second case, which is explained by both the higher complexity and the large number of timeouts.

@@

\subsection{Comparison with \ARMS}

@@

\subsection{Syntactic versus semantic evaluation}

>>>>

This section presents several experiments to evaluate the performance of \FAMA and the quality of the learned models. Whenever applicable, we will consider scenarios with both known and unknown plan horizon to draw conclusions at both levels of complexity.

\textcolor[rgb]{1.00,0.00,0.00}{After presenting the setup of the experiments in section \ref{setup}, we introduce three experiments that measure different aspects like the minimal number of traces necessary to obtain good quality models (section \ref{size_knowledge}), a comparison of the quality of models obtained by \FAMA compared to \ARMS (section \ref{compare_ARMS}) and an analysis of the quality of models when using a very small number of input traces in section \ref{minimal} In these three experiments, the quality of the models is measured using the syntactic-based precision and recall metrics presented in section \ref{syntactic_precision_recall}, that is, we measure the precision and recall of the learned models with respect to the GTM for each domain. Finally, the syntactic evaluation of section \ref{minimal} is compared against a semantic evaluation, i.e. how well the learned models are able to reproduce the input plan traces, in section \ref{semantic}.}

%We also devote one experiment to show the suitability of the novel evaluation metrics introduced in section \ref{sec:evaluation}.

\subsection{Setup}
\label{setup}

@@

\subsection{Impact of the size of the input knowledge}
\label{size_knowledge}

@@

Figure~\ref{fig:pspace_quality} displays \textcolor{red}{the average precision and recall of the 15 learned models} in the scenario with unknown plan horizon. As expected, the quality of the learned models is lower than when the horizon of the plan is known. \textcolor{red}{The higher complexity of this setting is also reflected in the appearance of some timeouts when solving the learning task. The first timeout is found in the \emph{grid} domain at $|\mathcal{T}| = 3$; the \emph{floortile} times out with $|\mathcal{T}| = 4$; and by the time $|\mathcal{T}|$ reaches 10 the number of domains were no solution is found is 6, adding the \emph{npuzzle, parking, rovers and zenotravel} domains.} We can observe in Figure~\ref{fig:pspace_quality} the opposite behaviour to Figure~\ref{fig:np_quality}; that is, we find a drop of the quality as the input knowledge increases. The drop in the score is caused by the increasing number of timeouts, meaning that no solution is found in many tasks within the given time-bound, and consequently a value of $0$ for precision and recall is assigned to these experiments. Figure \ref{fig:pspace_time}, on the other hand, \textcolor[rgb]{1.00,0.00,0.50}{\textbf{reflects that the computation time of the first case study is also higher than in the second case},} which is explained by both the higher complexity and the large number of timeouts.

@@

\subsection{Comparison with \ARMS}
\label{compare_ARMS}

@@

\subsection{Syntactic versus semantic evaluation}
\label{semantic}

### 2018-12-25 doc/aij18/major-revision/letter.tex
Update 25 Dec 11.00

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  - At the beginning of the evaluation you state the obvious - that the purpose is to evaluate the performance of FAMA and the quality of the models. At this stage to clarify the experimental section I suggest that you indicate, before detailing the set up, what would be success, for example how do you intend to show that your technique is better than or comparable to others? This will no doubt mean introducing the metrics you intend to use and giving an idea of success in terms of them. Also it may mean taking text from the start of the sections 6.2 - 6.5  into the first part of the evaluation section. This will however give a good rational for the 'set-up‚Äô, the choice of the particular experimental scenarios, and for the discussion of the results.
\end{mdframed}

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{PENDIENTE  .... y hay que revisar resultados, alguna cosa no cuadra ... }}

>>>>

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  - At the beginning of the evaluation you state the obvious - that the purpose is to evaluate the performance of FAMA and the quality of the models. At this stage to clarify the experimental section I suggest that you indicate, before detailing the set up, what would be success, for example how do you intend to show that your technique is better than or comparable to others? This will no doubt mean introducing the metrics you intend to use and giving an idea of success in terms of them. Also it may mean taking text from the start of the sections 6.2 - 6.5  into the first part of the evaluation section. This will however give a good rational for the 'set-up', the choice of the particular experimental scenarios, and for the discussion of the results.
\end{mdframed}

\textcolor{blue}{We have introduced a paragraph at the beginning of section 6 that gives an overview of the experiments presented in this section. The quality of the models (\emph{success} in the words of the reviewer) of the three first experiments is measured by the syntactic metrics introduced in the evaluation section; that is, the quality of the models is compared against the corresponding GTM. The last section presents a syntatic vs semantic evaluation of the learned models. The semantic evaluation measures the precision and recall of the models to reproduce the input plan traces. All this is explained in the introductory paragraph. With respect to moving text from the subsections of section 6 to section 5, we think the text of these subsections is particularly contextualized to the experiment in question and seems better to leave the text in section 6. Nevertheless, we have improved some explanations in section 6.}
